Manuscript

### 2022-11-14 analysis/manuscript.Rmd
reformatting for misc thing for final publications

```{r setup, include = FALSE}

options(scipen=999)
source("code/settings.R")
source("R/functions.R")
library(targets)
library(kableExtra)
library(DT)
library(knitr)
library(ggplot2)
library(kableExtra)
library(cowplot)
library(plotly)
library(plyr)
library(dplyr)
library(ggrepel)
library(viridis)
library(hrbrthemes)
library(ggpubr)
library(broom)
library(data.table)
library(xlsx)
```

@@

  theme_minimal() +
  theme(legend.text=element_text(size=11)) +
  #geom_text(aes(x=1,y=2,label=""),show.legend=F) +
  ggplot2::labs(x = paste0("Couple correlation"),
                y = paste("MR-estimate")) +
  theme(legend.position="bottom") + theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(corr_vs_MR_effects_dat, label_phenos==TRUE),
                  nudge_y = -0.35 - subset(corr_vs_MR_effects_dat, label_phenos==TRUE)$MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5 )

@@

@@

@@

  stat_compare_means(data = data_boxplot, comparisons = cmpr, label.y = c(0.6, 0.4, 0.5), method = "t.test" , paired =T) + #,
                     # label = "p.signif",
                     # symnum.args = list(cutpoints = c(0, 0.05, 1),
                     #                    symbols = c("*", "ns"))) +

@@

## Supplementary tables
write.xlsx_wrapper(final_table, file=supplementary_tables_file, sheetName="Supp Table 1 complete_summary", row.names=FALSE)
#write.xlsx_wrapper(AM_result_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 2 BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(nominally_sig_sex_differences, file=supplementary_tables_file, sheetName="Supp Table 3 nominally_sig_sex_diff", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 4 pheno_binned_corrs", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=supplementary_tables_file, sheetName="Supp Table 5 sig_corr_vs_MR", append = TRUE, row.names=FALSE)
write.xlsx_wrapper(sig_confounders, file=supplementary_tables_file, sheetName="Supp Table 3 sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=supplementary_tables_file, sheetName="Supp Table 4 paths_summary", append=TRUE, row.names=FALSE)

>>>>

```{r setup, include = FALSE, dev=c('png', 'pdf')}

options(scipen=999)
source("code/settings.R")
source("R/functions.R")
library(targets)
library(kableExtra)
library(DT)
library(knitr)
library(ggplot2)
library(kableExtra)
library(cowplot)
library(plotly)
library(plyr)
library(dplyr)
library(ggrepel)
library(viridis)
library(hrbrthemes)
library(ggpubr)
library(broom)
library(data.table)
library(xlsx)
library(rstatix)

knitr::opts_chunk$set(dev =c('png', 'pdf'))

@@

  theme_minimal() +
  theme(legend.text=element_text(size=11)) +
  #geom_text(aes(x=1,y=2,label=""),show.legend=F) +
  ggplot2::labs(x = paste0("Partner correlation"),
                y = paste("MR-estimate")) +
  theme(legend.position="bottom") + theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(corr_vs_MR_effects_dat, label_phenos==TRUE),
                  nudge_y = -0.35 - subset(corr_vs_MR_effects_dat, label_phenos==TRUE)$MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5 )

@@

sig_confounder_plus_SE <- left_join(sig_confounders, summ_C_data %>% dplyr::select(outcome_ID, corr_due_to_confounding_summ_SE), by = c("trait_ID"="outcome_ID")) %>%
dplyr::rename(summ_C_se = summ_C)

@@

stat.test <- data_boxplot %>% 
  t_test(beta ~ data, comparisons = cmpr, paired = T) %>%
  mutate(myformatted.p = paste0(pretty_round(p))) %>% 
  mutate(y.position = c(0.6, 0.4, 0.5))

@@

  stat_pvalue_manual(stat.test, label = "myformatted.p") +

  # stat_compare_means(data = data_boxplot, comparisons = cmpr, label.y = c(0.6, 0.4, 0.5), method = "t.test" , paired =T,
  #                   label = "p.format") +
  #                   # symnum.args = list(cutpoints = c(0, 0.05, 1),
  #                   #                    symbols = c("*", "ns"))) +

@@

## Supplementary tables
write.xlsx_wrapper(final_table, file=supplementary_tables_file, sheetName="Supp Table 1 complete_summary", row.names=FALSE)
#write.xlsx_wrapper(AM_result_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 2 BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(nominally_sig_sex_differences, file=supplementary_tables_file, sheetName="Supp Table 3 nominally_sig_sex_diff", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 4 pheno_binned_corrs", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=supplementary_tables_file, sheetName="Supp Table 5 sig_corr_vs_MR", append = TRUE, row.names=FALSE)
write.xlsx_wrapper(sig_confounder_plus_SE, file=supplementary_tables_file, sheetName="Supp Table 2 sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=supplementary_tables_file, sheetName="Supp Table 3 paths_summary", append=TRUE, row.names=FALSE)
